% LaTeX resume using res.cls
\documentclass[line,margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\addtolength{\textheight}{2in}
\addtolength{\textwidth}{.5in}
\addtolength{\voffset }{-.5in}
\addtolength{\oddsidemargin }{-.5in}
\setlength{\parindent}{0pt}

\renewcommand\familydefault{\sfdefault}
\renewcommand\labelitemi{--}

\begin{document}

\name{{\LARGE Alex Benedetto}}
\address{406.261.0065 $|$ alex@alex-benedetto.com $|$ https://linkedin.com/in/alex-benedetto $|$ github.com/wolfpack94}

\begin{resume}

\section{EDUCATION}
	{\bf Western Washington University}, Bellingham, WA \\
	Major: {\sl B.S.} Computer Science, {\small June 2017}\\
	Major GPA: 3.01\\
	{\sl Minor:} Mathematics\\
	{\sl Relevent Coursework: 305 {\small Analysis of Algorithms I}, 322 {\small Principles of Concurrent Programming},\\ 367 {\small Computer Networking I},
		 345 {\small Object-Oriented Programmings}, 330 {\small Database Systems},
		\\ 497H {\small Principles of Human-Centered Technology Design} }
\section{EXPERIENCE}

	%-- Personal projects --%
	{\sl Languages} -- {\sl Python, C, JavaScript, VBS, HTML, Java, C++, Autohotkey} \\
	{\sl Learning} -- {\sl Node.js, iOS Swift, Android Application Development}\\
	{\sl Databases} -- {\sl PostgreSQL, SQLite, MongoDB}\\
	{\sl Version Control} -- {\sl Git, SVN, CVS}\\
	\\
	{\sl Software Development Intern} -- {\bf The Walt Disney Company}\\ 
	{\footnotesize Seattle, WA $|$ April 2016 - present}\\
	\begin{itemize} \itemsep -2pt
		\item Working on data analysis of room activity around DTSS.
		\item Complete a D3.js visualization of occurrences of room activity.
	\end{itemize}
	{\sl Blockchain Development Engineer Intern} -- {\bf The Walt Disney Company}\\ 
	{\footnotesize Seattle, WA $|$ September 2016 - March 2016}\\
	\begin{itemize} \itemsep -2pt
		\item Assisted on the development of the Dragonchain Blockchain.
		\item Programmed extensively in Python and Apache Thrift.
		\item Worked on a recently released open source project under Disney.
		\item Learned about the ins and outs of blockchain and cryptocurrency.
	\end{itemize}
	{\sl PACs IT Analyst} -- {\bf Kalispell Regional Healthcare System} \\
	{\footnotesize Kalispell, MT $|$ June 2016 - September 2016}\\
	\begin{itemize} \itemsep -2pt
		\item Assisted in maintenance of the Picture Archiving and Communication System (PACs).
		\item Wrote programs to improve Radiologists workflow.
		\item Wrote and implement Visual Basic Scripts with Hostmonitor to automatically diagnose \\computer issues in the 300+ PC network.
		\item Assessed hardware issues and debug software designed for Radiologists.
	\end{itemize}
	{\sl Startup Web Developer} -- {\bf Eloi Supply Co.} \\
	{\footnotesize Kalispell, MT $|$  July 2013 - April 2015}\\
	\begin{itemize} \itemsep -2pt
		\item Front and back end web develpment with CSS3, HTML, Javascript.
		\item Maintained website, pushing updates when needed.
	\end{itemize}
	\section{PROJECTS}
		{\sl MightyMouse Mouse Remapping Software}
\begin{itemize}\itemsep -2pt
		\item PACs system mouse button remapping software designed for radiologists.
		\item Built with AutoHotkey for Windows.
		\item Remaps mouse buttons based on which types of studies a radiologist is reading.
		\item Sped up workflow by getting rid of Logitech gaming software profile switching.
	\end{itemize}
	{\sl PyCat}
	\begin{itemize}\itemsep -2pt
		\item Python implementation of the popular netcat.
		\item Includes chat server that can handle multiple clients using multi-threading.
		\item Includes chat client/server able to serve multiple connections and provide direct messaging.
	\end{itemize}



\section{ACTIVITIES and AWARDS}
	\begin{itemize} \itemsep -3pt
	\item Nominee for the Walt Disney Company Best of Technology award
	\item Association for Computing Machinery national member
	\item Invent Coworking Startup Challenge, WWU Hackathon
	\end{itemize}

\end{resume}

\end{document}
